\documentclass[letterpaper,1pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome}

%Custom code for links--------------------------

\hypersetup{
    colorlinks=false,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
    pdftitle={Yash Verma's CV},
    pdfpagemode=FullScreen,
    }

\urlstyle{same}


% Redefinition, symbol included in link:
\let\orighref\href
\renewcommand{\href}[2]{\orighref{#1}{#2\,\faExternalLink}}

%Custom code for links--------------------------


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{-4pt}
\renewcommand{\footrulewidth}{-4pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.575in}
\addtolength{\evensidemargin}{-0.575in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.6in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    #1 \vspace{-1.1pt}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2.75pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-3.0pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-13pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=1pt]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-7pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{Yash Verma's CV}
\author{Yash Verma(yash10019coder)}

\begin{document}
%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Yash Verma}} & \href{https://www.linkedin.com/in/yash10019coder}{\faicon{linkedin} yash10019coder}\\
  \href{mailto:yashverma10019.work@gmail.com}{\faicon{envelope} yashverma10019.work@gmail.com}& \href{https://github.com/yash10019coder}{\faicon{github} yash10019coder} \\
  \faicon{phone} +918957557113 & \href{https://twitter.com/yash10019coder}{\faicon{twitter} yash10019coder}
\end{tabular*}
% \itemsep-0.2em
% \vspace{-10pt}

\section*{Summary}
Experienced Full Stack Developer with a strong background in developing backend and optimizing scalable android apps, fault-tolerant systems. Proficient in Go, Java, Python, and Kotlin with extensive experience in CI/CD, database management, and cloud-based solutions. Passionate about crafting efficient and reliable software solutions, with a proven track record in delivering high-quality projects within dynamic, fast-paced environments.

%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Indian Institute of Information Technology, Lucknow}{Lucknow}
{Bachelor of Information Technology;  CGPA: 8.32}{Apr. 2020 -- Apr. 2024}
\resumeItem{Relevant Courses}{Data Structures \& Algorithms, Operating System, System Design, DBMS, Object Oriented Programming, Distributed Systems, Software Management, Design Patterns.}
\resumeSubHeadingListEnd

% \vspace{1pt}

%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{\href{https://0chain.net}{0chain}}{Cupertino, CA (Remote)}
{Full Stack Engineer}{Feb 2022 -- Present}

\resumeItemListStart
% \begin{itemize}[]
\resumeItem {\textbf{Tech Stacks}: \textbf{Kotlin, Java, Golang, AndroidSDK, NDK, Github actions, Elastic Search, Gin, Grafana, Helm}.}
\resumeItem {Developed two Android apps, \textbf{Bolt} and \textbf{Vult}, increasing the Android user base by \textbf{20\%} for decentralized storage using \textbf{ZCN cryptocurrency}.}
\resumeItem {Designed and implemented a \textbf{UAT test suite} for enterprise blobbers, reducing production bugs by \textbf{30\%} and improving release quality.}
\resumeItem {Led and mentored two junior developers, improving \textbf{code quality} by \textbf{40\%} and ensuring \textbf{95\%} on-time delivery through effective \textbf{scrum leadership}.}
\resumeItem{Migrated and refactored gosdk to decrease app size by \textbf{50\%}, also helped cross platform teams with the migration.  }
\resumeItem{Integrated \textbf{Elastic Search} for processing and \textbf{indexing transactions} from blockchain which decreased the fetch time by \textbf{10x}.}
\resumeItem{Incorporated \textbf{release pipelines} for \textbf{android apps} reducing manual labour and increasing release time by \textbf{70\%.}}
% \end{itemize}
\resumeItemListEnd

\resumeSubheading
{Google Summer of Code Oppia Foundation \href{https://docs.google.com/document/d/150Yk14Cxmy8OAbSSwgP1aXDBLo1b8HtuIhmrRhzEWU4/edit}{link}}{Remote}
{Open Source Contributor - Gsoc Student}{June 2021 -- Sept 2022}
\resumeItemListStart
% \begin{itemize}[itemsep=1pt, parsep=0pt]
\resumeItem {\textbf{Tech Stack}: \textbf{Kotlin, GitHub Actions, JUnit, UIAutomator, Gradle, Bazel, AndroidSDK}.}
\resumeItem {Pioneered \textbf{CI/CD pipeline enhancements}, reducing \textbf{build and deployment time} by \textbf{40\%}, leading to faster release cycles.}
\resumeItem {Spearheaded \textbf{Gradle to Bazel transition}, increasing \textbf{build efficiency} by \textbf{60\%}, accelerating development cycles.}
\resumeItem {Expanded the application’s reach by integrating \textbf{tablet support}, resulting in a \textbf{25\%} increase in the potential user base.}
\resumeItem {Orchestrated and refined over \textbf{90 automated tests}, increasing \textbf{codebase stability} by \textbf{30\%} and reducing production bugs by \textbf{20\%}.}
% \end{itemize}
\resumeItemListEnd

\resumeSubheading
{\href{https://gnome.org}{Gnome Foundation}}{Remote}
{Open Source Contributor}{Sept 2021 -- Feb 2022}
\resumeItemListStart
% \begin{itemize}[itemsep=1pt, parsep=0pt]
\resumeItem {Tech Stack \textbf{C, XML, GTK+}}
\resumeItem {Added a new feature in the \textbf{pathbar of Nautilus file manager}, improving \textbf{user efficiency} by \textbf{20\%} by enabling seamless opening of folders and files.}
\resumeItem {Designed and implemented a new button using \textbf{XML}, enhancing \textbf{user interaction} by \textbf{15\%} through improved interface functionality.}
% \end{itemize}
\resumeItemListEnd

% \resumeSubheading
% {BSHAPP \href{https://github.com/yash10019coder/bshapp}{Link of App}}{Andhra Pradesh}{Android Freelance Developer}{May 2021 -- June 2021}
% \begin{itemize}[itemsep=1pt, parsep=0pt]
%   \item Added support for \textbf{multiple languages}, expanding the app's user base by \textbf{30\%} and enhancing accessibility in diverse markets.
%   \item Implemented \textbf{Jetpack Navigation} with single activity and multi-fragment architecture, improving app performance by \textbf{25\%}.
%   \item Integrated \textbf{REST API} with \textbf{Retrofit}, reducing data retrieval time by \textbf{20\%} and improving HTTP request efficiency.

% \end{itemize}

\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
\begin{itemize}[leftmargin=*, itemsep=1pt, parsep=0pt]

  \item \href{https://github.com/yash10019coder/ParkingLotBackend}{\textbf{Parking Lot Management System}}: Developed a RESTful API using \textbf{Node.js}, \textbf{Express.js}, and \textbf{MongoDB} to efficiently manage parking spaces. Integrated \textbf{Winston} for logging and conducted unit and integration testing with \textbf{Jest}.
  \item \href{https://github.com/yash10019coder/TravelSpringBoot}{\textbf{Trip Feedback System}}: Designed a feedback system for \textbf{Travelers} and \textbf{Transport Managers} with secure feedback submission, user authentication, using \textbf{Spring Framework}.
        % \item \href{https://github.com/yash10019coder/festify-android}{\textbf{Festify}}: Hackathon and event management multi-module Android app with NodeJs backend and MongoDB database.
  \item \href{https://github.com/0chain/HelloWorld-Android}{\textbf{Hello World}}: Android application showcasing 0Chain blockchain storage SDK, implemented in Kotlin.
        % \item \href{https://github.com/yash10019coder/Wake-Lock}{\textbf{Wake-Lock}}: Runs a sticky service in the background which adds a partial wake lock to your screen.
        % \item \href{https://github.com/yash10019coder/AutomatedWindowManager}{\textbf{Automated Window Manager}}: A CLI tool to automate window management in Linux.
        % \item \href{https://github.com/yash10019coder/backup-system-ubuntu}{\textbf{Backup System Ubuntu}}: A bash script to back up apt, snap, and other config files.
        % \item \href{https://github.com/yash10019coder/Gui-Automator}{\textbf{GUI-Automator}}: Python script for downloading, sorting, and extracting files from Google Drive.
        % \item \href{https://github.com/yash10019coder/Whats-App}{\textbf{What's App Clone}}: Android chat app featuring Google and email authentication.
        % \item \href{https://github.com/yash10019coder/Video-Chatting}{\textbf{Video Chatting}}: Android app for video conferencing using Jitsi Meet API with a secure server setup.
        % \item \href{https://github.com/yash10019coder/resume}{\textbf{My Resume}}: Automated deployment of resume updates using GitHub Actions and GCP to Google Drive.

\end{itemize}

%
%--------PROGRAMMING SKILLS------------
\section{Technical Skills}
\begin{itemize}[leftmargin=*, itemsep=1pt, parsep=0pt]
  \selectfont\small
  \setlength\itemsep{0em}
  \setlength\parsep{0em}
  \item \textbf{Programming \& Scripting}: Java, Go, Kotlin, Python, JavaScript, C, C++, SQL, Bash
  \item \textbf{Frameworks \& Tools}: SpringBoot, Gin, AndroidSDK, Dagger/Hilt, RxJava, Retrofit, Okhttp, Android Jetpack, Express, Git, Gradle, Bazel
  \item \textbf{Testing \& Databases}: JUnit, Mockito, Robolectric, Espresso, UIAutomator, MySQL, MongoDB, Realm, Postgres, Firebase
  \item \textbf{DevOps, Cloud \& Security}: Linux, GCP, Docker, Kubernetes, Github Actions, CI/CD, Prometheus, Grafana, Loki, Helm
\end{itemize}

%-------------------------------------------
\end{document}
