\documentclass[letterpaper,1pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome}

%Custom code for links--------------------------

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
    pdftitle={Yash Verma's CV},
    pdfpagemode=FullScreen,
    }

\urlstyle{same}


% Redefinition, symbol included in link:
\let\orighref\href
\renewcommand{\href}[2]{\orighref{#1}{#2\,\faExternalLink}}

%Custom code for links--------------------------


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{-5pt}
\renewcommand{\footrulewidth}{-5pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-3.3pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-9pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{Yash Verma's CV}
\author{Yash Verma(yash10019coder)}

\begin{document}
%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Yash Verma}} & \href{https://www.linkedin.com/in/yash10019coder}{\faicon{linkedin} yash10019coder}\\
  \href{mailto:yashverma10019.work@gmail.com}{\faicon{envelope} yashverma10019.work@gmail.com}& \href{https://github.com/yash10019coder}{\faicon{github} yash10019coder} \\
  \faicon{phone} +918957557113 & \href{https://twitter.com/yash10019coder}{\faicon{twitter} yash10019coder}
\end{tabular*}
\itemsep-0.2em
\vspace{-5pt}

%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Indian Institute of Information Technology, Lucknow}{Lucknow}
{Bachelor of Information Technology;  CGPA: 8.32}{Apr. 2020 -- Apr. 2024}
\resumeItem{Relevant Courses}{Data Structures \& Algorithms, Operating System, System Design, DBMS, Object Oriented Programming, Distributed Systems, Software Management, Design Patterns.}
\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{\href{https://0chain.net}{0chain}}{Cupertino, CA (Remote)}
{Android Engineer}{Feb 2022 -- Present}

\begin{itemize}
  \item \textbf{Tech Stacks}: Kotlin, Java, Golang, AndroidSDK, NDK, Github actions.
  \item Developing \textbf{two} Android apps Bolt, Vult for a decentralized storage built upon ZCN cryptocurrency.
  \item Reduced \textbf{Bolt} and \textbf{Vult} app size by \textbf{12\%} by migrating from \textbf{Realm} to \textbf{Room} database.
  \item  Written \textbf{E2E} and \textbf{unit tests}, Along with developing an automated pipeline for build and release.
  \item Leading and mentoring two junior devs in daily tasks and overseeing scrum meetings and code reviews.
\end{itemize}


\resumeSubheading
{Google Summer of Code Oppia Foundation \href{https://docs.google.com/document/d/150Yk14Cxmy8OAbSSwgP1aXDBLo1b8HtuIhmrRhzEWU4/edit}{link}}{Remote}
{Open Source Contributor - Gsoc Student}{June 2021 -- Sept 2022}
\begin{itemize}[itemsep=1pt, parsep=0pt]
  \item \textbf{Tech Stack}: Kotlin, GitHub Actions, JUnit, UIAutomator, Gradle, Bazel, AndroidSDK.
  \item Pioneered CI/CD pipeline enhancements, expediting build and deployment processes.
  \item Spearheaded Gradle to Bazel transition, amplifying build efficiency by an order of magnitude.
  \item Expanded the application's reach by integrating tablet support, boosting potential user base.
  \item Orchestrated and refined over 90 automated tests, elevating codebase stability and reliability.
\end{itemize}


\resumeSubheading
{\href{https://gnome.org}{Gnome Foundation}}{Remote}
{Open Source Contributor}{Sept 2021 -- Feb 2022}
\resumeItemListStart
\resumeItem{Tech Stack}{C, XML, GTK+}
\resumeItem{GTK4}
{Added a new feature in the pathbar of \href{https://gitlab.gnome.org/GNOME/nautilus}{\textbf{Nautilus}} file manager to open folders and files with other applications seamlessly.}
\resumeItem{Xml}
{Made the wireframe and program of the new button with Xml.}
\resumeItemListEnd

\resumeSubheading
{BSHAPP \href{https://github.com/yash10019coder/bshapp}{Link of App}}{Andhra Pradesh}{Android Freelance Developer}{May 2021 -- June 2021}
\resumeItemListStart
\resumeItem{Multi Language}
{Added Support for multiple Languages.}
\resumeItem{Jetpack Navigation}
{Used Jetpack Navigation with single activity and multi fragment artitecture.}
\resumeItem{Retrofit}
{Integerated \textbf{REST} api with Retrofit to make \textbf{HTTP} requests.}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
\begin{itemize}[leftmargin=*, itemsep=1pt, parsep=0pt]
  \item \href{https://github.com/yash10019coder/Wake-Lock}{\textbf{Wake-Lock}}: Runs a sticky service in background which adds a partial wake lock to your screen.
  \item \href{https://github.com/yash10019coder/AutomatedWindowManager}{\textbf{Automated Window Manager}} : A cli tool to automate window management in Linux.
  \item \href{https://github.com/yash10019coder/backup-system-ubuntu}{\textbf{Backup System Ubuntu}}: A bash script to get all of the apt, snap and other etc config files.
  \item \href{https://github.com/0chain/HelloWorld-Android}{\textbf{Hello World}}: Android application showcasing 0Chain blockchain storage SDK, implemented in Kotlin.
  \item \href{https://github.com/yash10019coder/festify-android}{\textbf{Festify}}: Hackathon and event management multi-module Android app with NodeJs backend and MongoDB database.
  \item \href{https://github.com/yash10019coder/Gui-Automator}{\textbf{GUI-Automator}}: Python script for downloading, sorting, and extracting files from Google Drive.
  \item \href{https://github.com/yash10019coder/Whats-App}{\textbf{What's App Clone}}: Android chat app featuring Google and email authentication.
  \item \href{https://github.com/yash10019coder/Video-Chatting}{\textbf{Video Chatting}}: Android app for video conferencing using Jitsi Meet API with a secure server setup.
  \item \href{https://github.com/yash10019coder/resume}{\textbf{My Resume}}: Automated deployment of resume updates using GitHub Actions and GCP to Google Drive.
\end{itemize}

%
%--------PROGRAMMING SKILLS------------
\section{Technical Skills}
\begin{itemize}
  \setlength\itemsep{0em}
  \setlength\parsep{0em}
  \item \textbf{Programming \& Scripting}: Java, Kotlin, Python, JavaScript, C, C++, SQL, Bash
  \item \textbf{Frameworks \& Tools}: AndroidSDK, Dagger/Hilt, RxJava, Retrofit, Okhttp, Android Jetpack, Express, Git, Gradle, Bazel
  \item \textbf{Testing \& Databases}: JUnit, Mockito, Robolectric, Espresso, UIAutomator, MySQL, MongoDB, Realm, SQLite, Firebase
  \item \textbf{DevOps, Cloud \& Security}: Linux, GCP, Docker, Kubernetes, Github Actions, CI/CD pipelines, Nginx, TLS, SSL, Bash Scripting
\end{itemize}


%-------------------------------------------
\end{document}
