\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome}

%Custom code for links--------------------------

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
    pdftitle={Yash Verma's CV},
    pdfpagemode=FullScreen,
    }

\urlstyle{same}


% Redefinition, symbol included in link:
\let\orighref\href
\renewcommand{\href}[2]{\orighref{#1}{#2\,\faExternalLink}}

%Custom code for links--------------------------


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{Yash Verma's CV}
\author{Yash Verma(yash10019coder)}

\begin{document}
%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
	\textbf{{\Large Yash Verma}} & \href{https://www.linkedin.com/in/yash10019coder}{\faicon{linkedin} yash10019coder}\\
	\href{mailto:yashverma10019@gmail.com}{\faicon{envelope} yashverma10019@gmail.com}& \href{https://github.com/yash10019coder}{\faicon{github} yash10019coder} \\
	\faicon{phone} +918957557113 & \href{https://twitter.com/yash10019coder}{\faicon{twitter} yash10019coder}
\end{tabular*}
%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Indian Institute of Information Technology, Lucknow}{Lucknow}
{B.Tech in Information Technology;  \textbf{CG-PA: 8.32/10}}{Apr. 2020 -- Apr. 2024}
\resumeSubHeadingListEnd
%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading
{\href{https://0chain.net}{0chain}}{Cupertino, CA (Remote)}
{Android Engineer}{Feb 2022 -- Present}
\resumeItemListStart
\resumeItem{Tech Stack}{Kotlin, Java, Gradle, AndroidSDK, Retrofit, Room, Dagger/Hilt, Golang.}
\resumeItem{XML}
{Converted \textbf{figma wire frames} into XML layouts}
\resumeItem{Database migration}
{Migrated from \textbf{Realm} to \textbf{Room} database which decreased the app size by \textbf{5MB 12\%}.}
\resumeItem{Bash Scripting  }
{Added a pre-commit hook for the code-base to run es lint checks and typescript checks which reduced the lint and type errors by \textbf{100\%} in the codebase.}
\item {Handled both the android apps of the organization made consistent releases and also made numerous features from scratch.}
\resumeItemListEnd
\resumeSubheading
{Google Summer of Code Oppia Foundation \href{https://docs.google.com/document/d/150Yk14Cxmy8OAbSSwgP1aXDBLo1b8HtuIhmrRhzEWU4/edit}{link}}{Remote}
{Gsoc Student}{Aug 2021 -- Sept 2022}
\resumeItemListStart
\resumeItem{Tech Stack}{Kotlin, GitHub Actions, JUnit, UIAutomator, Gradle, Bazel, Starlark, AndroidSDK}
\resumeItem{\href{https://docs.google.com/document/d/150Yk14Cxmy8OAbSSwgP1aXDBLo1b8HtuIhmrRhzEWU4/edit}{Technical Design Docs}}{Designed and architect-ed the whole \textbf{CI/CD} architecture for the builds. }
\resumeItem{Release Automation}{Automated \textbf{signing}, \textbf{building}, \textbf{testing} and \textbf{uploading} to Google Play along with automated cherry-picks.}
\resumeItem{Gradle,Bazel}
{Helped in build system migration from \textbf{Gradle} to \textbf{Bazel} which increases build speeds by \textbf{10x}.}
\resumeItem{Tablet Support}
{ Added support for tablet devices in the app which increased the user base by \textbf{20\%}. }
\resumeItem{TDD(Test Driven Development)}
{Written \textbf{70+} Unit Tests, \textbf{20+} Instrumentation and End-to-end tests in \textbf{Espresso}, \textbf{Robolectric} and \textbf{UIAutomator} with \textbf{JUnit} as test runner for Android.}
\resumeItemListEnd
\resumeSubheading
{\href{https://gnome.org}{Gnome Foundation}}{Remote}
{Open Source Contributor}{Sept 2021 -- Feb 2022}
\resumeItemListStart
\resumeItem{Tech Stack}{C, XML, GTK+}
\resumeItem{GTK4}
{Added a new feature in the path bar of \href{https://gitlab.gnome.org/GNOME/nautilus}{\textbf{Nautilus}} file manager to open folders and files with other applications seamlessly.}
\resumeItem{XML}
{Made the wire frame and program of the new button with XML.}
\resumeItemListEnd
\resumeSubHeadingListEnd
%-----------PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart
\resumeItem{\href{https://github.com/yash10019coder/festify-android}{Festify}}
{Hackathon and event management \textbf{Android} app with \textbf{NodeJs} \href{https://github.com/yash10019coder/festify-node-server}{Back-end link} and \textbf{MongoDB database.}}
\resumeItem{\href{https://github.com/yash10019coder/Whats-App}{What's App Clone}}
{Peer to Peer and group chat Android App with thread-based model and equipped with Google and email authentication.}
\resumeItem{\href{https://github.com/yash10019coder/Video-Chatting}{Video-Chatting}}
{Android app made with \href{https://github.com/jitsi/jitsi-meet}{\textbf{jitsi-meet-api}} also deployed a custom scalable video server on Ubuntu VM along with setting up \textbf{Nginx} server and \textbf{TLS} layer to make it secure.}
\resumeSubHeadingListEnd
%--------PROGRAMMING SKILLS------------
\section{Technical Skills}
\resumeSubHeadingListStart
\resumeItem{Programming Languages}{: Java, Kotlin, Python, JavaScript, C, C++, SQL, bash, Golang}
\resumeItem{Technologies/Frameworks}{: Linux, AndroidSDK, Dagger/Hilt, Android Jetpack, NodeJS, Docker, Google Cloud, GitHub actions, CI/CD pipelines, Express, MongoDB, Realm, Git, MySQL, Firebase, Gradle, Bazel, JSON, Regex}
\resumeItem{Coursework}{Data Structures \& Algorithms, Operating System, System Design, DBMS, Object Oriented Programming, Distributed Systems, Software Management, Design Patterns.}
\resumeSubHeadingListEnd
% \section{Position of Responsibilities}
% \begin{itemize}
% 	\item \textbf{Onboarding mentor} at Oppia Foundation.
% 	\item Member of \textbf{Developer Workflow} Team at Oppia Foundation.
% 	\item Member of \textbf{Android Welfare} Team at Oppia Foundation.
% 	\item Senior Member at \textbf{Axios, IIITLucknow}.
% \end{itemize}
%-------------------------------------------
\end{document}
