\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

%Custom code for links--------------------------

\usepackage{fontawesome}

% Redefinition, symbol included in link:
\let\orighref\href
\renewcommand{\href}[2]{\orighref{#1}{#2\,\faExternalLink}}

%Custom code for links--------------------------


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%



\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
	\textbf{{\Large Yash Verma}} & Email : \href{mailto:yashverma10019@gmail.com}{yashverma10019@gmail.com}\\
	\href{https://www.linkedin.com/in/yash10019coder}{Linkedin: www.linkedin.com/in/yash10019coder} & \href{https://github.com/yash10019coder}{Github: https://github.com/yash10019coder}
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Indian Institute of Information Technology, Lucknow}{Lucknow}
{Bachelor of Information Technology;  CGPA: 8.32}{Apr. 2020 -- Apr. 2024}
\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{\href{https://0chain.net}{0chain}}{Cupertino, CA}
{Android Engineer}{Feb 2022 -- Present}
\resumeItemListStart
\resumeItem{MVVM}
{Migrated and refactored the code to follow the  \textbf{MVVM} architecture.}

\resumeItem{Dagger/Hilt}
{Used them for \textbf{dependency injection} for third party libraries and classes.}

\resumeItem{Xml}
{Converted the \textbf{figma wireframes} to high quality xml layouts and used \textbf{Gosdk} to write backend code in \textbf{java} for them.}

\resumeItem{Realm}
{Used the \textbf{Realm} database to store data and \textbf{sync} with \textbf{online} database.}

\resumeItem{Retrofit}
{Made API endpoints in \textbf{Android} with \textbf{Retrofit} to make http requests with \textbf{TLS} encryption and parsed the data with \textbf{gson}.}

\resumeItem{Okhttp}
{Used \textbf{okhttp} as a http client for making requests and also used a \textbf{Interceptor} to log requests.}

\resumeItem{Bash Scripting  }
{Added a pre-commit hook for codebase to run eslint checks and typescript checks which reduced the lint and type errors by \textbf{100\%} in the codebase.}
\resumeItemListEnd

\resumeSubheading
{\href{https://oppia.org}{Oppia Foundation} \href{https://github.com/oppia/oppia-android}{Github Link} \href{https://github.com/oppia/oppia-android/commits?author=yash10019coder}{[Link to Merged PRs]}}{Mountain View, CA}
{Open Source Contributor Android}{Aug 2021 -- Present}
\resumeItemListStart
\resumeItem{Gradle,Bazel}
{Helped in build system migration from \textbf{gradle} to \textbf{bazel}.}
\resumeItem{Tablet Support}
{Created new new \textbf{fragments} which are wrapped inside their own \textbf{activities} in mobile so that both open seamlessly in mobile and tablets supporting \textbf{multiple} screen sizes. }
\resumeItem{MVVM+MVP}
{Followed \textbf{MVVM}(Model View View Model)+\textbf{MVP}(Model View Presenter) architecture to code all of the activities and fragments.}
\resumeItem{TDD(Test Driven Development)}
{Written \textbf{70+} Unit Tests, \textbf{20+} Instrumentation and End-to-end tests in \textbf{Espresso}, \textbf{Robolectric} and \textbf{UIAutomator} with \textbf{JUnit} as test runner for Android.}
\resumeItemListEnd

\resumeSubheading
{\href{https://gnome.org}{Gnome Foundation}}{US}
{Open Source Contributor}{Sept 2021 -- Feb 2022}
\resumeItemListStart
\resumeItem{GTK4}
{Added a new feature in the pathbar of \href{https://gitlab.gnome.org/GNOME/nautilus}{\textbf{Nautilus}} file manager to open folders and files with other applications seamlessly.}
\resumeItem{Xml}
{Made the wireframe and program of the new button with Xml.}
\resumeItemListEnd

\resumeSubheading
{BSHAPP \href{https://github.com/yash10019coder/bshapp}{Link of App}}{Android Freelance Developer}{Andhra Pradesh}{May 2021 -- June 2021}
\resumeItemListStart
\resumeItem{Multi Language}
{Added Support for multiple Languages.}
\resumeItem{Jetpack Navigation}
{Used Jetpack Navigation with single activity and multi fragment artitecture.}
\resumeItem{Retrofit}
{Integerated \textbf{REST} api with Retrofit to make \textbf{HTTP} requests.}
\resumeItemListEnd
\resumeSubHeadingListEnd

-----------Awards and achivements--------------
\section{Awards and Achievements}
\begin{itemize}
	\item \textbf{\href{https://summerofcode.withgoogle.com/programs/2022/projects/zGrrUdxM}{Google Summer of Code 2022}} {at Oppia Foundation.}
	      \begin{itemize}
		      \item Android Release Automation for signing, building, testing and uploading to Google Play.
	      \end{itemize}
\end{itemize}

%-----------PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart
\resumeItem{\href{https://github.com/yash10019coder/festify-android}{Festify}}{Hackathon and event management \textbf{Android} app with \textbf{NodeJs} \href{https://github.com/yash10019coder/festify-node-server}{Backend link} and \textbf{MongoDB database.}}
{Open source python library for financial data analysis and machine learning for finance.}
\resumeItem{\href{https://github.com/yash10019coder/Gui-Automator}{GUI-Automator}}
{Written in \textbf{python} to download files from google drive and automatically arranging sorting and extracting them.}
\resumeItem{\href{https://github.com/yash10019coder/Whats-App}{What's App Clone}}
{Peer to Peer and group chat Android App with thread based model and equipped with Google and email authentication.}
\resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Technical Skills}
\resumeSubHeadingListStart
\item{
            \textbf{Programming Languages}{: Java, Kotlin, Python, JavaScript/NodeJS, C, C++, SQL, bash}
      }
\item{
            \textbf{Technologies/Frameworks}{: AndroidSDK, Docker, Kubernetes, Google Cloud, Express, MongoDB, Realm, Git, MySQL, Firebase, Gradle, Bazel, Nginx, JSON, Regex}
      }
\resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
