\documentclass[letterpaper,1pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

%Custom code for links--------------------------

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
    pdftitle={Yash Verma's CV},
    pdfpagemode=FullScreen,
    }

\urlstyle{same}

\usepackage{fontawesome}

% Redefinition, symbol included in link:
\let\orighref\href
\renewcommand{\href}[2]{\orighref{#1}{#2\,\faExternalLink}}

%Custom code for links--------------------------


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{Yash Verma's CV}
\author{Yash Verma(yash10019coder)}

\begin{document}
\small

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Yash Verma}} & Email : \href{mailto:yashverma10019@gmail.com}{yashverma10019@gmail.com}\\
  Linkedin: \href{https://www.linkedin.com/in/yash10019coder}{www.linkedin.com/in/yash10019coder} & Github: \href{https://github.com/yash10019coder}{https://github.com/yash10019coder}
\end{tabular*}

\vspace{-5pt}

%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{\href{https://0chain.net}{0chain}}{Cupertino, CA (Remote)}
{Android Engineer}{Feb 2022 -- Jun 2023}
\resumeItemListStart
\resumeItem{MVVM}
{Migrated and refactored the code to follow the  \textbf{MVVM} clean architecture with \textbf{Dagger/Hilt}.}

% \resumeItem{Dagger/Hilt}
% {Used them for \textbf{dependency injection} for third party libraries and classes.}

\resumeItem{Figma wireframes}
{Converted the \textbf{figma wireframes} to high quality xml layouts \textbf{optimized} for \textbf{different} sizes.}

\resumeItem{Database migration}
{Migrated from \textbf{Realm} to \textbf{Room} database which decreased the app size by \textbf{5MB 12\%}.}

\resumeItem{Paging}
{Implemented \textbf{pagination} for the API's to load data in chunks using \textbf{Paging 3} library.}

\resumeItem{Bash Scripting}{Added a pre-commit hook for codebase to run eslint checks and typescript checks which reduced the lint and type errors by \textbf{100\%} in the codebase.}

% \resumeItem{Unit Tests}{Implemented \textbf{unit tests} for the codebase using \textbf{Mockito} and \textbf{Robolectric} which increased the code coverage by \textbf{70\%}.}

% \resumeSubItem{E2E Tests}{Implemented \textbf{E2E tests} for the codebase using \textbf{Espresso} and \textbf{MockWebServer} which increased the code coverage by \textbf{90\%}.}


% Commneting out these two for now.
% \resumeItem{\href{https://play.google.com/store/apps/details?id=network.zus.bolt}{Bolt}, \href{https://play.google.com/store/apps/details?id=network.zus.vult}{Vult}}{Managed and maintained the Android apps of the organization's apps development with and releases.}

% \resumeItem{\href{https://github.com/0chain/HelloWorld-Android}{Hello World}}{Developed a sample app demonstrating the \textbf{0chain} sdk with \textbf{clean architecture} and \textbf{coroutines}.}

\resumeItem{CI/CD}{Implemented \textbf{CI/CD} pipelines for the \textbf{Android} apps with \textbf{github actions} and \textbf{Google Cloud Platform} to automatically upload the new version of the app to \textbf{Google Play}.}

\resumeItemListEnd

\vspace{-10pt}
\subsection*{[\href{https://play.google.com/store/apps/details?id=network.zus.bolt&hl=en-US&ah=HGd0D5DYnNgKbjuxWV1AaOVbuyc}{Bolt Application}]}
\begin{itemize}

  \vspace{-5pt}
  \item Led the development of the \textbf{"Bolt" cryptocurrency app}, known for its \textbf{lightning-fast 100\% finality transactions} in under 2 seconds.
  \item Implemented \textbf{split-key technology} for \textbf{enhanced security}, providing a convenient and secure alternative to traditional hardware wallets.
  \item Designed an \textbf{intuitive user interface} for \textbf{stake management}, \textbf{reward visualization}, and seamless \textbf{ZCN to ETH swapping}.
  \item Collaborated across teams to integrate \textbf{RESTful APIs}, optimizing user experience through \textbf{responsive design}.
  \item Migrated from \textbf{Realm to Room database}, reducing app size by \textbf{12\%} and improving efficiency.
  \item Conducted \textbf{comprehensive unit and end-to-end testing}, raising code coverage by \textbf{70\%} and \textbf{90\%} respectively.
  \item Maintained a \textbf{99.7\% crash-free rate} through vigilant \textbf{bug fixing} and \textbf{performance optimization}.
  \item Contributed to \textbf{technical documentation} to ensure clarity and promote team collaboration.
\end{itemize}

\vspace{-10pt}
\subsection*{[\href{https://play.google.com/store/apps/details?id=network.zus.vult&hl=en-US&ah=HGd0D5DYnNgKbjuxWV1AaOVbuyc}{Vult Application}]}
\begin{itemize}
  \vspace{-5pt}
  \item Spearheaded the development of the \textbf{"Vult" app}, empowering users with \textbf{encrypted data ownership} and \textbf{seamless sharing capabilities}.
  \item Designed and implemented an \textbf{Encrypted folder} for automatic data protection of \textbf{private photos} and \textbf{sensitive files}.
  \item Collaborated with \textbf{UI/UX designers} to create an \textbf{intuitive interface} for managing encrypted and shared files, photos, and videos.
  \item Integrated \textbf{RESTful APIs} for transparent tracking of \textbf{file storage}, challenges passed, and \textbf{blockchain event recording}.
  \item Integrated \textbf{end-to-end encryption protocols}, ensuring \textbf{secure data sharing} among users.
  \item Leveraged reactive programming with \textbf{RxJava} for enhanced app \textbf{responsiveness} and user interaction.
  \item Contributed to \textbf{automated testing strategies}, maintaining high-quality standards.
  \item Actively participated in \textbf{agile methodologies}, driving \textbf{iterative improvements} and \textbf{timely feature releases}.
\end{itemize}



\resumeSubheading
{Google Summer of Code Oppia Foundation \href{https://docs.google.com/document/d/150Yk14Cxmy8OAbSSwgP1aXDBLo1b8HtuIhmrRhzEWU4/edit}{link}}{Remote}
{Gsoc Student}{May 2022 -- Sept 2022}
\resumeItemListStart
\resumeItem{Design Docs}{Designed and architected the whole ci/cd artitecutre for the builds. }
\resumeItem{Pipelines/Github workflows}{Auto-triggers builds for \textbf{alpha}, \textbf{beta} and \textbf{test} releases, uploads and signs the binary to google drive, gcp bucket and google play store tracks.}
\resumeItem{Cherry Picks}{Automated cherry picking workflow which automatically merges the cherry picks on the flavour branch.}
\resumeItem{Issue tracker releases}{Automated logging of each build and release steps of the release on the github issue along with workflows triggering and from commenting on the issue.}
\resumeItemListEnd
\begin{itemize}
  \item \textbf{Android Release Automation} for \textbf{signing}, \textbf{building}, \textbf{testing} and \textbf{uploading} to Google Play.
  \item Writing custom \textbf{kotlin} scripts for most common tasks like building the \textbf{aab}, \textbf{signing} the aab, \textbf{uploading} the aab to Google Play.
  \item Use of \textbf{github actions} along with the custom \textbf{kotlin} scritps exectued with \textbf{bazel} for \textbf{cd pipelines} for alpha, beta and nigthly releases on daily cron jobs.
\end{itemize}


\resumeSubheading
{\href{https://oppia.org}{Oppia Foundation} \href{https://github.com/oppia/oppia-android}{Github Link} \href{https://github.com/oppia/oppia-android/commits?author=yash10019coder}{[Link to Merged PRs]}}{Mountain View, CA (Remote)}
{Open Source Contributor Android}{June 2021 -- April 2022}
\resumeItemListStart
\resumeItem{Gradle,Bazel}
{Helped in build system migration from \textbf{gradle} to \textbf{bazel} which increases build speeds by \textbf{10x}.}
\resumeItem{Tablet Support}
{Created new new \textbf{fragments} which are wrapped inside their own \textbf{activities} in mobile so that both open seamlessly in mobile and tablets supporting \textbf{multiple} screen sizes. }
\resumeItem{MVVM+MVP}
{Followed \textbf{MVVM}(Model View View Model)+\textbf{MVP}(Model View Presenter) architecture to code all of the activities and fragments.}
\resumeItem{TDD(Test Driven Development)}
{Written \textbf{70+} Unit Tests, \textbf{20+} Instrumentation and End-to-end tests in \textbf{Espresso}, \textbf{Robolectric} and \textbf{UIAutomator} with \textbf{JUnit} as test runner for Android.}
\resumeItem{Mentoring}{Successfully mentored \textbf{3+} students in the \textbf{Android} repository and ]textbf{onboarded} them as \textbf{collaborators}.}
\resumeItem{Wiki}{Written wiki github documentation on \textbf{Protobuf} for which greatly improved the understanding of the \textbf{protobuf} library in the \textbf{repository}.}
\resumeItem{GSOC}{Helped a GSOC student in \textbf{bazel} errors and reviewed the PR.}
\resumeItemListEnd

\resumeSubheading
{\href{https://gnome.org}{Gnome Foundation}}{Remote}
{Open Source Contributor}{Sept 2021 -- Feb 2022}
\resumeItemListStart
\resumeItem{GTK4}
{Added a new feature in the pathbar of \href{https://gitlab.gnome.org/GNOME/nautilus}{\textbf{Nautilus}} file manager to open folders and files with other applications seamlessly.}
\resumeItem{Xml}
{Made the wireframe and program of the new button with Xml.}
\resumeItemListEnd

\resumeSubheading
{BSHAPP \href{https://github.com/yash10019coder/bshapp}{Link of App}}{Andhra Pradesh}{Android Freelance Developer}{May 2021 -- June 2021}
\resumeItemListStart
\resumeItem{Multi Language}
{Added Support for multiple Languages.}
\resumeItem{Jetpack Navigation}
{Used Jetpack Navigation with single activity and multi fragment artitecture.}
\resumeItem{Retrofit}
{Integerated \textbf{REST} api with Retrofit to make \textbf{HTTP} requests.}
\resumeItemListEnd
\resumeSubHeadingListEnd

% -----------Awards and achivements--------------
% \section{Awards and Achievements}
% \begin{itemize}
% 	\item \textbf{\href{https://summerofcode.withgoogle.com/proposals/details/nQ9e5GZr}{Google Summer of Code 2022}} {at Oppia Foundation.}
% 	      \begin{itemize}
% 		      \item Android Release Automation for signing, building, testing and uploading to Google Play.
% 		      \item Writing custom \textbf{kotlin} scripts for most common tasks like building the aab, signing the aab, uploading the aab to Google Play.
% 		      \item Use of \textbf{github actions} along with the custom \textbf{kotlin} scritps exectued with \textbf{bazel} for \textbf{cd pipelines} for alpha, beta and nigthly releases on daily cron jobs.
% 	      \end{itemize}
% \end{itemize}

%-----------PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart
\resumeItem{\href{https://github.com/0chain/HelloWorld-Android}{Hello World}}{A application to demonstrate the use of \textbf{0Chain} decentralized blockchain storage SDK in \textbf{Android} app with coroutines and clean-architecture in \textbf{Kotlin}.}
\resumeItem{\href{https://github.com/yash10019coder/festify-android}{Festify}}{Hackathon and event management \textbf{Android} app with \textbf{NodeJs} \href{https://github.com/yash10019coder/festify-node-server}{Backend link} and \textbf{MongoDB database.}}
{Open source python library for financial data analysis and machine learning for finance.}
\resumeItem{\href{https://github.com/yash10019coder/Gui-Automator}{GUI-Automator}}
{Written in \textbf{python} to download files from google drive and automatically arranging sorting and extracting them.}
\resumeItem{\href{https://github.com/yash10019coder/Whats-App}{What's App Clone}}
{Peer to Peer and group chat Android App with thread based model and equipped with Google and email authentication.}
\resumeItem{\href{https://github.com/yash10019coder/Video-Chatting}{Video-Chatting}}
{Android app made with \href{https://github.com/jitsi/jitsi-meet}{jitsi-meet-api} also deployed a custom scalable video server on Ubutnu VM along with setting up nginx server and TLS layer to make it secure.}
\resumeItem{\href{https://github.com/yash10019coder/resume}{My-Resume}}{Personal Resume with seperate tracks and \textbf{cd pipeline} with \textbf{github actions} and \textbf{Google Cloud Platform} to automatically upload the new version of the resume to \textbf{Google Drive}.}
\resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Technical Skills}
\resumeSubHeadingListStart
\item{
            \textbf{Programming Languages}{: Java, Kotlin, Python, JavaScript, C, C++, SQL, bash}
      }
\item{
            \textbf{Technologies/Frameworks}{: AndroidSDK, Dagger/Hilt, RxJava, Retrofit, Okhttp, Android Jetpack, Express, Git, Gradle, Bazel, JSON, Regex}
      }
\item{
            \textbf{Testing}{: JUnit, Mockito, Robolectric, Espresso, UIAutomator}
      }
\item {
            \textbf{Databases}{: MySQL, MongoDB, Realm, SQLite, Firebase}
      }
\item{
            \textbf{Devops/Cloud}{: Linux, Google Cloud Platform, Docker, Kubernetes, Github Actions, CI/CD pipelines, Nginx, TLS, SSL, Bash Scripting}
      }
\resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Indian Institute of Information Technology, Lucknow}{Lucknow}
{Bachelor of Information Technology;  CGPA: 8.32}{Apr. 2020 -- Apr. 2024}
\resumeItem{Relevant Courses}{Data Structures \& Algorithms, Operating System, System Design, DBMS, Object Oriented Programming, Distributed Systems, Software Management, Design Patterns.}
\resumeSubHeadingListEnd

\section{Position of Responsibilities}
\begin{itemize}
  \item \textbf{Onboarding mentor} at Oppia Foundation.
  \item Member of \textbf{Developer Workflow} Team at Oppia Foundation.
  \item Member of \textbf{Android Welfare} Team at Oppia Foundation.
  \item Senior Member at \textbf{Axios, IIITLucknow}.
\end{itemize}
%-------------------------------------------
\end{document}
